---
title: "StringSearchInFiles.R"
author: "S. Schiwek"
date: '2020-05-01'
output:
  pdf_document:
    toc: yes
  html_document:
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

## Libraries

***

```{r}
library(readr)
library(stringr)
library(knitr)

```

## Functions

***

### Function that searches string in file and returns how often it appeared
```{r}
findFiles <- function(file, string = string, myignorecase = T){
  Code <- read_file(paste0(file))
  #result.grepl<-grepl(pattern = string,x = Code,ignore.case = myignorecase)
  result.count <- str_count(Code, regex(string, ignore_case = myignorecase))
  return(data.frame(resultcount = result.count))
}

```

### Display the area surroundings of string in file
```{r}
getSurroundings <- function(string = 'iasviewability', file, area = 200, myignorecase = T){
  Code <- read_file(file)
  result.count <- str_count(Code, regex(string, ignore_case = myignorecase))
  result <- vector(mode = "character", length = result.count)
  stringchars <- nchar(string)
  position <- 0
  #return(result)
  for(i in 1:result.count){
    #find position of ith appearance
    loopcode <-
      substring(Code,
                position + ((i - 1) < 0)*stringchars,
                nchar(Code)
                )
    positionupdate <- regexpr(pattern = string,
                              text = loopcode,
                              ignore.case = myignorecase
                              )
    position <- position + positionupdate
    result[i] <- substring(text = loopcode,
                           first = max(positionupdate - area, 1),
                           last = min(positionupdate + area + stringchars,
                                      nchar(loopcode)
                                      )
                           )
  }
  return(result)
}

```

### Function stringSearch
Arguments       |   
----------------|-------------------------
folder          | folder you want to search
string          | what you are searching for inside the code in Regex
myignorecase    | should your search be case insensivite?
datefilter      | add a 'date modified' filter, if you want to. Only result younger than this will be shown
pattern         | (Default: R, python and SQL -files)
surroundingarea | characters of surrounding area

```{r}
stringSearch <-
  function(
    folder = 'C:/nanoathenareports',
    string = 'iasviewability',
    myignorecase = T,
    datefilter = NULL,
    pattern = '\\.R$|\\.py$|\\.r$|\\.sql|\\.SQL',
    surroundingarea = 20
  ){
    # list of ALL files in folder
    # recursive: Search also sub folders
    filelist <- list.files(folder,
                           pattern = pattern,
                           recursive = T,
                           full.names = T)
    # filter out files, that match criteria
    # datefilter:
    if(!is.null(datefilter)){
      filelist <- filelist[difftime(datefilter, file.info(filelist)$mtime) < 0]}
    
    # sort by 'last modified' date
    filelist <- filelist[order(file.info(filelist)$mtime, decreasing = T)]
    
    # Does file-content match string?
    fileSearch <- lapply(X = filelist, FUN = findFiles, string = string)
    fileSearch <- do.call(what = rbind, args = fileSearch)
    
    #
    fulllist <- data.frame(fileslist = filelist,
                           appearancecount = fileSearch$resultcount,
                           stringsAsFactors = F
    )
    
    # Filter only files, that contain string
    results.tmp <- fulllist[fulllist$appearancecount > 0, ]
    
    # show surroundings of that string
    a <- lapply(X = results.tmp$fileslist,
                FUN = getSurroundings,
                string = string,
                area = surroundingarea)
    names(a) <- results.tmp$fileslist
    returnlist <- list()
    returnlist[[1]] <- data.frame(results.tmp,
                                  lastchange = format(file.info(results.tmp$fileslist)$mtime),
                                  stringsAsFactors = F
    )
    returnlist[[2]] <- a
    names(returnlist) <- c('files','surroundings')
    return(returnlist)
  }

```

### enter folder you want to search
```{r}
# source(file = paste0(getwd(),'/StringSearchInFiles/functions.R'))
```


## Results

***

### Files with that pattern 
Contains:

* Actual File name 
* Count of appearances of this pattern inside that file.
* Date when that file was last modified

```{r}
result <- 
  stringSearch(
    folder = '/Users/ullijeratsch/rprog/ausstellung_andreas',
    string = 'iasviewability'
  )

knitr::kable(result$files,
              col.names = c("File name",
                           "Count of appearances",
                           "Date last modified")
             )
```

### Show surrounding areas of appearances
```{r}
for (myfile in 1:length(result$surroundings)) {
  cat(paste0('\r\n\r\n','File: ', names(result$surroundings[myfile]), '\r\n\r\n'))
  for(i in 1:length(result$surroundings[[myfile]])){
    cat(paste0('\r\n\r\n # of appearance: ', i, '\r\n\r\n', result$surroundings[[myfile]][i]))
  }
}

```
